What is long-distance dispersal? And a taxonomy of dispersal events\\ \vspace{2cm}

### 2016-10-09 Manuscript/MS- What is LDD.tex
Edited Discussion refs and Intro.

Two-dimensional patterns in the \textit{P. mahaleb} seed rain and the individual seed shadows, accurately tracked with DNA-based genotyping methods, thus reflect the complex effects of frugivore foraging, habitat preferences and heterogeneous landscapes. This situation is probably generalizable to other plant--frugivore interactions (Morales and Carlo, 2006) where the combined spatial dynamics of habitat use and digestion processes determine complex seed shadows (Jordano et al., 2007; see Dennis and Westcott, [REF]; see Nathan, [REF]). Much of this complexity can be adequately handled by mechanistic models (Nathan et al., 2002; Morales and Carlo, 2006) incorporating very simple rules (Viswanathan et al., 2002). For example, earlier results (Jordano 2007) showed that the dispersal distances contributed by \textit{P. mahaleb} frugivores closely map the spacing patterns of fruiting trees, but only up to a certain distance ($\leq100 m$; Fig. 10.3a in Jordano 2007). Beyond this, frugivores were probably responding to other major landscape elements (e.g. rock outcrops, forest edges, large patches of open grassland, etc) that cause the fat tail of the seed dispersal distribution, adding more frequent LDD events than expected from a Brownian random walk pattern generated by a tracking of the crops of the fruiting trees. For instance, the long flights performed by \textit{T. viscivorus} (Jordano and Schupp, 2000) frequently faced the pine forest edge, at distances $\geq100 m$ of most \textit{P. mahaleb} fruiting trees. If these medium-sized birds are selecting habitat with tall woody vegetation (e.g. pines $\geq6 m$ height), then they should be perceiving a much more patchy landscape, and thus requiring longer flights, than for example, small warblers seeking vegetation cover $<0.5 m$ (Fig. 10.3b in Jordano 2007).

>>>>

Two-dimensional patterns in the \textit{P. mahaleb} seed rain and the individual seed shadows, accurately tracked with DNA-based genotyping methods, thus reflect the complex effects of frugivore foraging, habitat preferences and heterogeneous landscapes. This situation is probably generalizable to other plant--frugivore interactions where the combined spatial dynamics of habitat use and digestion processes determine complex seed shadows \citep{Westcott:200,Jordano:2007,Nathan:2008is}. Much of this complexity can be adequately handled by mechanistic models \citep{Nathan:2002a} incorporating very simple rules \citep{Guttal:2011hs}. For example, earlier results \citep{Jordano:2007a} showed that the dispersal distances contributed by \textit{P. mahaleb} frugivores closely map the spacing patterns of fruiting trees, but only up to a certain distance ($\leq$100 m) \citep[Fig. 10.3a in][]{Jordano:2007a}. Beyond this, frugivores were probably responding to other major landscape elements (e.g. rock outcrops, forest edges, large patches of open grassland, etc) that cause the fat tail of the seed dispersal distribution, adding more frequent LDD events than expected from a Brownian random walk pattern generated by a tracking of the crops of the fruiting trees. For instance, the long flights performed by \textit{T. viscivorus} \citep{Jordano:2000ft} frequently faced the pine forest edge, at distances $\geq$100 m of most \textit{P. mahaleb} fruiting trees. If these medium-sized birds are selecting habitat with tall woody vegetation (e.g. pines $\geq$6 m height), then they should be perceiving a much more patchy landscape, and thus requiring longer flights, than for example, small warblers seeking vegetation cover $<$0.5 m \citep[Fig. 10.3b in][]{Jordano:2007a}.
